Paper_analyses

### 2021-07-26 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd
test
solved jelkas comment

data<- lastopened

@@

??ma
?stats::filter
tmp.df4_full_stim_downs_jun2021_with_behnew%>%
  subset(ssid == 310 & tNo == 10)%>%
  ggplot(aes(timerezero3,zoo::rollmean(pup_velocity, k = 3, fill = NA)))+
  geom_line()+
  geom_line(aes(y = pup_velocity), color = 'red')+
  geom_smooth(se = F)

tmp.df4_full_stim_downs_jun2021_with_behnew%>%
  subset(ssid == 310 & tNo == 15)%>%
  ggplot(aes(timerezero3,pup_basCor))+
  geom_point()+
  # geom_line(aes(y = pup_velocity), color = 'red')+
  geom_smooth(se = F)

@@

tmp.df4_full_stim_downs_jun2021_60bins <- tmp.df4_full_stim_downs_jun2021_60bins %>%
  # subset(!is.na(mediansplit_sample_arousal2))%>%
  # subset(valencearousal_outliers == TRUE) %>%
  # subset(!is.na(mediansplit_sample_arousal2))%>%
  group_by(ssid, tNo) %>%
  mutate(pup_velocity = (abs(lag(pup_basCor)-pup_basCor)/abs(lag(timerezero3)-timerezero3)))
  # mutate(pup_velocity_peak = max(pup_velocity, na.rm = TRUE))

@@

tmp.df4_full_stim_downs_jun2021_60bins<- tmp.df4_full_stim_downs_jun2021_60bins%>%
  # subset(ssid == 331 & tNo ==40)%>%
  group_by(ssid, tNo)%>%
  arrange(ssid,tNo, timerezero3)%>%
  mutate(pup_vel_smooth = zoo::rollmean(pup_velocity, k = 3, fill = NA))

@@

velocity timecourse
```{r}
# let's test the interaction term
nbins<- unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
range(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)

@@

>>>>

data<- last opened

@@

??ma
?stats::filter
tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ssid == 310 & tNo == 10)%>%
  ggplot(aes(timerezero3,pup_vel_smooth))+
  geom_line()+
  geom_point()
  # geom_line(aes(y = pup_velocity),Ç color = 'red')
  # geom_smooth(se = F)

tmp.df4_full_stim_downs_jun2021_60bins%>%
    subset(ssid == 320 & tNo == 20)%>%
  ggplot(aes(timerezero3,pup_basCor))+
  geom_point()+
  geom_line()+
  geom_line(aes(y = pup_vel_smooth), color = 'red')+
  geom_point(aes(y = pup_vel_smooth), color = 'red')
  # geom_line(aes(y = pup_velocity), color = 'red')+
  # geom_smooth(se = F)

@@

tmp.df4_full_stim_downs_jun2021_60bins <- tmp.df4_full_stim_downs_jun2021_60bins %>%
  # subset(!is.na(mediansplit_sample_arousal2))%>%
  # subset(valencearousal_outliers == TRUE) %>%
  # subset(!is.na(mediansplit_sample_arousal2))%>%
  group_by(ssid, tNo) %>%
  mutate(pup_velocity = (abs(lag(pup_basCor)-pup_basCor)/abs(lag(timerezero3)-timerezero3)))%>%
  mutate(pup_velocity_dir = ((lag(pup_basCor)-pup_basCor) / abs(lag(timerezero3)-timerezero3)))
  # mutate(pup_velocity_peak = max(pup_velocity, na.rm = TRUE))

@@

tmp.df4_full_stim_downs_jun2021_60bins$four<- paste0(tmp.df4_full_stim_downs_jun2021_60bins$mediansplit_sample_arousal2,
                                                     paste0(tmp.df4_full_stim_downs_jun2021_60bins$mediansplit_sample_valence2))

paste0(tmp.df4_full_stim_downs_jun2021_60bins$mediansplit_sample_arousal2)

# unique(tmp.df4_full_stim_downs_jun2021_60bins)

  tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ssid_num < 500)%>%
  subset(!is.na(mediansplit_sample_valence2))%>%
  group_by(ssid, tNo)%>%
  arrange(ssid,tNo, timerezero3)%>%
   ggplot(aes(timerezero3, pup_basCor, color = four))+
  stat_smooth(se = F)
  # geom_line(aes(y = pup_vel_smooth), color = 'red')

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ssid_num < 500)%>%
  subset(!is.na(mediansplit_sample_valence2))%>%
  group_by(ssid, tNo)%>%
  arrange(ssid,tNo, timerezero3)%>%
   ggplot(aes(timerezero3, pup_velocity, color = four))+
  stat_smooth(se = T)
  # stat_smooth(aes(y = pup_velocity_dir),se = F, linetype = 'dashed')
  # geom_line(aes(y = pup_vel_smooth), color = 'red')

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ssid_num < 500)%>%
  subset(!is.na(mediansplit_sample_valence2))%>%
  group_by(ssid, tNo)%>%
  arrange(ssid,tNo, timerezero3)%>%
   ggplot(aes(timerezero3, pup_velocity_dir, color = four))+
  # stat_summary(fun = mean, geom = 'line')
  stat_smooth(se = T)
  # stat_smooth(aes(y = pup_velocity_dir),se = F, linetype = 'dashed')
  # geom_line(aes(y = pup_vel_smooth), color = 'red')

@@

```{r}  
  tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ssid_num < 500)%>%
  subset(!is.na(mediansplit_sample_valence2))%>%
  group_by(ssid, tNo)%>%
  arrange(ssid,tNo, timerezero3)%>%
   ggplot(aes(timerezero3, pup_basCor, color = four))+
  stat_smooth(se = F)
  geom_line(aes(y = pup_vel_smooth), color = 'red')

  tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ssid_num < 500)%>%
  subset(!is.na(mediansplit_sample_valence2))%>%
  group_by(ssid, tNo)%>%
  arrange(ssid,tNo, timerezero3)%>%
   ggplot(aes(timerezero3, pup_vel_smooth, color = four))+
  stat_smooth(se = F)
  geom_line(aes(y = pup_vel_smooth), color = 'red')

  tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ssid_num < 500)%>%
  subset(!is.na(mediansplit_sample_valence2))%>%
  group_by(ssid, tNo)%>%
  arrange(ssid,tNo, timerezero3)%>%
   ggplot(aes(timerezero3, pup_basCor, color = four))+
  stat_smooth(se = F)
  geom_line(aes(y = pup_vel_smooth), color = 'red')

is velocity correlated with puypil amplitude
```{r}
require(tidyverse)

tmp.df4_full_stim_downs_jun2021_60bins %>%
  group_by(stimIAPS)%>%
  mutate(cor_vel_pup = cor(pup_vel_smooth,pup_basCor, use = 'complete'))%>%
  mutate(vel_max = max(pup_vel_smooth,na.rm = TRUE))%>%
  summarise_if(is.numeric, mean,na.rm = TRUE)%>%
  ggplot(aes(vel_max,pup_basCor))+
  geom_point()+
  geom_smooth(method = 'lm')+
  ggpubr::stat_cor()

```
velocity timecourse
```{r}
# let's test the interaction term
nbins<- unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
range(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)

@@

# https://masterr.org/r/how-to-find-consecutive-repeats-in-r/
timecourse_60bin_result_df_vel$test<- NULL

timecourse_60bin_result_df_vel$test <- rle(timecourse_60bin_result_df_vel$p_ar < 0.05)
# View(runs)
# 
# runs[2]
# myruns = which(runs$values == TRUE & runs$lengths >= 3)
